An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-07-10 EconGrowth.Rnw
Now including LINEX resample plots in the paper.

The LINEX model is given in Equation~\ref{eq:LINEX}. 
Parameters $a_0$ and $c_t$ were estimated using the \texttt{nls} function 
in \texttt{R} \citep{R}. 
Figure~\ref{fig:LINEXq_Params_Graph} shows values and 95\% confidence intervals 
for the parameters for the LINEX model (with $q$).

>>>>

The LINEX model is given in Equation~\ref{eq:LINEX}. 
Parameters $a_0$ and $c_t$ were estimated using the \texttt{nls} function 
in \texttt{R} \citep{R}.

Figures~\ref{fig:LINEXq_Resample_Graph}--\ref{fig:LINEXu_Resample_Graph}
show the coefficients estimated from resampled data.

<<LINEXq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $q$) resampling results.", eval=TRUE>>=
linexResamplePlot(energyType="Q")
@

<<LINEXx_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $x$) resampling results.", eval=TRUE>>=
linexResamplePlot(energyType="X")
@

<<LINEXu_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="LINEX model (with $u$) resampling results.", eval=TRUE>>=
linexResamplePlot(energyType="U")
@

Figure~\ref{fig:LINEXq_Params_Graph} shows values and 95\% confidence intervals 
for the parameters for the LINEX model (with $q$).
